Tree size, (microhabitat)?, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-08-15 manuscript/climate_sensitivity_draft.Rmd
fixed equation
fixed equation
update, knit ms

$$ DBH_Y  = DBH_{2008} - 2*[\sum_{year=Y}^{2008} (r_{ring, Y}:r_{ring,2008}) - r_{bark,Y} + r_{bark,2008}] $$

@@

We identified droughts within the time period 1950-2009, defining drought [@slette_how_2019] as events where peak growing season climatic conditions were anomalously dry relative to the long-term record and where tree growth was substantially reduced for at least some components of the community. To identify years with widespread reductions in tree growth, we used the pointRes package [@R-pointRes] in R (version 3.5.3) to determine drought periods based on trees' drought resistance, which is defined as the ratio between the performance during and before the disturbance [@lloret_components_2011]. Candidate drought years were defined if >50% of the cored trees experienced <30% growth in a year compared to the previous 5 years for at least three species-canopy class combinations, where canopy class included canopy (dominant and co-domiant) and subcanopy (suppressed and intermediate). **[this includes 1991- why did we drop it? [issue #52](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/52)]** Candidate droughts were then cross-validated with the regional Palmer Drought Severity Index (PDSI) values [**source?**] **(and MJJA PET-PRE (droughts identified in Helcoski)?)**. **[This paragraph needs work. See issue #52](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/52). Put climate criteria first.]**

[averaged resistance values for 1964-1966]

>>>>

$$ DBH_Y  = DBH_{2008} - 2*\left[\sum_{year=Y}^{2008} (r_{ring, Y}:r_{ring,2008}) - r_{bark,Y} + r_{bark,2008}\right] $$

@@

We identified droughts within the time period 1950-2009, defining drought [@slette_how_2019] as events where peak growing season climatic conditions were anomalously dry relative to the long-term record and where tree growth was substantially reduced for at least some components of the community. To identify years with widespread reductions in tree growth, we used the pointRes package [@R-pointRes] in R (version 3.5.3) to determine drought periods based on trees' drought resistance, which is defined as the ratio between the performance during and before the disturbance [@lloret_components_2011]. Specifically, we looked at the ratio between annual basal area increment (BAI) in the year of the drought to average annual BAI in the 5 preceding years.  *Candidate drought years were defined if >50% of the cored trees experienced <30% growth in a year compared to the previous 5 years for at least three species-canopy class combinations, where canopy class included canopy (dominant and co-domiant) and subcanopy (suppressed and intermediate).* **[this includes 1991- why did we drop it? [issue #52](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/52)]** Candidate droughts were then cross-validated with the regional Palmer Drought Severity Index (PDSI) values [**source?**] **(and MJJA PET-PRE (droughts identified in Helcoski)?)**. **[This paragraph needs work. See issue #52](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/52). Put climate criteria first.]**
